Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-05-30 docs/paper/paper.Rmd
update fig org

```{r vis-forecasts, fig.cap = "Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in the Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom,  by forecast horizon (one to four weeks). Incidence rates are shown on a log scale. 30\\%, 60\\%, and 90\\% credible intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time.", out.width = "95%", fig.height = 12, fig.width = 9}
locs <- c("United Kingdom", "Germany", "Slovakia", "Italy", "Poland", "Greece")

@@

```{r plot-coverage, fig.height = 9, fig.width = 9, out.width = "95%"}
hlines <- data.table(
  range = paste0(ranges, "% interval"), nominal = ranges / 100
)

@@

plot_interval_score <- relative_interval_score |>
  copy() |>
  DT(,
    .(relative_interval_score = median(relative_interval_score)),
    by = c("horizon", "range")
  ) |>
  ggplot() +
  aes(x = range / 100, y = relative_interval_score, col = as.factor(horizon)) +
  geom_hline(yintercept = 1, linetype = 2) +
  geom_point(size = 1.2) +
  geom_line(alpha = 0.8) +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(trans = "log", breaks = seq(1, 4, by = 0.2)) +
  scale_colour_brewer(palette = "Accent") +
  theme_scoringutils() +
  labs(
    x = "Quantile", y = "Median relative interval score",
    col = "Forecast horizon (weeks)"
  )

(((plot_cov_levels /
  plot_interval_score)  +
  plot_layout(heights = c(3, 1), guides = "collect")
) |
  plot_cov_quantile) +
  plot_layout(guides = "collect", widths = c(1, 2)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.box="vertical", legend.margin = margin()
  )
```

>>>>

```{r vis-forecasts, fig.cap = "Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in the Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom,  by forecast horizon (one to four weeks). Incidence rates are shown on a log scale. 30\\%, 60\\%, and 90\\% credible intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time.", out.width = "95%", fig.height = 12, fig.width = 12}
locs <- c("United Kingdom", "Germany", "Slovakia", "Italy", "Poland", "Greece")

@@

```{r plot-coverage, fig.height = 12, fig.width = 18, out.width = "95%"}
hlines <- data.table(
  range = paste0(ranges, "% interval"), nominal = ranges / 100
)

@@

plot_interval_score <- relative_interval_score |>
  copy() |>
  DT(,
    .(relative_interval_score = median(relative_interval_score)),
    by = c("horizon", "range")
  ) |>
  ggplot() +
  aes(x = range / 100, y = relative_interval_score, col = as.factor(horizon)) +
  geom_hline(yintercept = 1, linetype = 2) +
  geom_point(size = 1.2) +
  geom_line(alpha = 0.8) +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(
    trans = "log", breaks = c(seq(1, 2, by = 0.2), seq(2.4, 4, by = 0.4))
  ) +
  scale_colour_brewer(palette = "Accent") +
  theme_scoringutils() +
  labs(
    x = "Quantile", y = "Median relative interval score",
    col = "Forecast horizon (weeks)"
  )

(((plot_cov_levels /
  plot_interval_score)  +
  plot_layout(heights = c(3, 1), guides = "collect")
) |
  plot_cov_quantile) +
  plot_layout(guides = "collect", widths = c(1, 2)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin()
  )
```
